The language of generalization: Probability, vagueness, and interaction

### 2018-02-08 paper/case2-habituals.Rmd
refactor code in first half of habituals

```{r habituals-prior-data}
annualRates = list("5 years" = 1/5, "2 years" = 1/2,
                   "year" = 1, "6 months" = 2, "2 months" = 6,
                   "month" = 12, "2 weeks" = 26 ,"week" = 52)

d.hab.priors <- read.csv(paste(project.path, "data/habituals/priors/", "habituals-priors.csv", sep = ""))

d.hab.priors <- d.hab.priors %>%
  mutate(comparisonTime_men = as.character(comparisonTime_men),
         comparisonTime_women = as.character(comparisonTime_women),
         item = as.character(item),
         item = ifelse(item == "sell things on eBay", "sells things on eBay", item)) %>%
  rowwise() %>%
  mutate(
    mixture_male = nPersons_men / comparisonNum_men,
    mixture_female = nPersons_women / comparisonNum_women,
    dayRate_male = ifelse(comparisonTime_men == "week", nInstances_men / 7,
                   ifelse(comparisonTime_men == "month", nInstances_men / 30,
                   ifelse(comparisonTime_men == "year", nInstances_men / 365,
                   ifelse(comparisonTime_men == "5 years", 
                          nInstances_men / (5*365), -99)))),
    dayRate_female = ifelse(comparisonTime_women == "week", nInstances_women / 7,
                   ifelse(comparisonTime_women == "month", nInstances_women / 30,
                   ifelse(comparisonTime_women == "year", nInstances_women / 365,
                   ifelse(comparisonTime_women == "5 years", 
                          nInstances_women / (5*365), -99)))),
    annualRate_male = dayRate_male * 365,
    annualRate_female = dayRate_female * 365
  )

d.hab.priors.filtered <- filter(d.hab.priors, 
       !(
         (mixture_male == 0) ||   (mixture_female == 0) ||   
           (dayRate_male == 0) ||   (dayRate_female == 0)  )
       )
```

```{r habituals-prior-forwardsample}
# this is basically bootstrapping and combining using the structured model

d.hab.priors.samples <- data.frame()
for (i in 1:10){

  d.hab.priors.samples <- bind_rows(
    d.hab.priors.samples,
    d.hab.priors.filtered %>% 
    select(workerid, item, starts_with("annualRate"), 
           starts_with("mixture")) %>%
    rowwise() %>%
    mutate(
      stable_male = rbinom(n = 1, size = 1, prob = mixture_male),
       freq_male = ifelse(stable_male == 1, annualRate_male, 0.007),
       stable_female = rbinom(n = 1, size = 1, prob = mixture_female),
       freq_female = ifelse(stable_female == 1, annualRate_female, 0.007)
       ) %>%
    select(item, freq_male, freq_female) %>%
    gather(gender, val, freq_male, freq_female) %>%
  mutate(gender = gsub("freq_", "", gender))
  )
}

```{r habituals-prior-model}
hab.prior.bda.model <- '
var betaShape = function(p){
  return {a: p.g * p.d, b: (1-p.g) * p.d}
};

var model = function(){
	var mixtureParams = {
		male: {
      g: uniformDrift({a: 0, b: 1, width: 0.2}),
      d: uniformDrift({a: 0, b: 100, width: 5})
    },
		female: {
      g: uniformDrift({a: 0, b: 1, width: 0.2}),
      d: uniformDrift({a: 0, b: 100, width: 5})
    }
	};

	var mixtureShapes = {
		male: betaShape(mixtureParams.male),
		female: betaShape(mixtureParams.female)
	};

	mapData({data: data.mixture}, function(d){
    Beta(mixtureShapes[d.gender]).score(d.val) == -Infinity ? display(JSON.stringify(d)) : null
     // display(Beta(mixtureShapes[d.gender]).score(d.val))
		observe(Beta(mixtureShapes[d.gender]), d.val)
	})

	var stableFrequency = {
		male: {
			mu: uniformDrift({a: -5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:10, width: 1})
		},
		female: {
			mu: uniformDrift({a:-5, b:10, width: 2}),
			sigma: uniformDrift({a:0, b:10, width: 1})
		}
	}

	mapData({data: data.frequency}, function(d){
    Gaussian(stableFrequency[d.gender]).score(d.logval) == -Infinity ? 
        display(JSON.stringify(d)) : null
    // display(Gaussian(stableFrequency[d.gender]).score(d.logval))
		observe(Gaussian(stableFrequency[d.gender]), d.logval)
	})

	var existenceProb = {
		male: beta(mixtureShapes.male),
		female: beta(mixtureShapes.female)
	};

	var freqWhenPresent = {
		male: gaussian(stableFrequency.male),
		female: gaussian(stableFrequency.female)
	}

  var marginalFreq = {
    male: flip(existenceProb.male) ? freqWhenPresent.male : -5,
    female: flip(existenceProb.female) ? freqWhenPresent.female : -5,
  }

  return {
    mix_mean_male : mixtureParams.male.g,
    mix_mean_female : mixtureParams.female.g,
    mix_samplesize_male : mixtureParams.male.d,
    mix_samplesize_female : mixtureParams.female.d,
    stableFreq_mean_male : stableFrequency.male.mu,
    stableFreq_mean_female :stableFrequency.female.mu,
    stableFreq_sd_male : stableFrequency.male.sigma,
    stableFreq_sd_female :stableFrequency.female.sigma,
    marginalFreq_NA_male: marginalFreq.male,
    marginalFreq_NA_female: marginalFreq.female
  }
}
'
```

```{r habituals-prior-model-run, cache = T, eval = F}

n_samples <- 20000
items <- levels(factor(d.hab.priors.filtered$item))

rs.habituals.bda.prior <- data.frame()

for (it in items){

 df.prior.toPass <- list(
   frequency = d.hab.priors.filtered %>%
      filter(item == it) %>%
      select(item, starts_with("annualRate")) %>%
      gather(gender, val, -item) %>%
      mutate(gender = gsub("annualRate_", "", gender),
             logval = log(val)),
   mixture = d.hab.priors.filtered %>% 
      filter(item == it) %>%
      select(item, starts_with("mixture")) %>%
      gather(gender, val, -item) %>%
      mutate(gender = gsub("mixture_", "", gender)) %>%
      rowwise() %>%
      mutate(val = ifelse(val == 1, 0.9999, 
                          ifelse(val == 0, 0.000001, val)))
  )

  rs <- webppl(program_code = hab.prior.bda.model,
       model_var = "model",
       inference_opts = list(method = "MCMC", samples = n_samples,
                             burn = n_samples / 2),
       data = df.prior.toPass,
       data_var = "data")

  rs.habituals.bda.prior <- bind_rows(
    rs.habituals.bda.prior, 
    rs %>% 
      mutate(item = it) %>% 
      separate(Parameter, into = c("Variable", "Parameter", "Gender"))
  )
}
save(rs.habituals.bda.prior, 
     file = paste(project.path,  "models/habituals/results/", 
                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
                  ".RData", sep = ""))

```{r habituals-prior-model-parameters, fig.width = 5}
n_samples <- 20000
items <- levels(factor(d.hab.priors.filtered$item))

load(file = paste(project.path,  "models/habituals/results/", 
                  "habituals-prior-", n_samples, "_burn", n_samples/2 , 
                  ".RData", sep = ""))

example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
                       "climbs mountains", "hikes", "runs", 
                       "wears a suit", "wears a watch", "wears socks", 
                       "writes poems", "goes to the movies", "plays the banjo"
                       )

rs.habituals.bda.prior.summary <- rs.habituals.bda.prior %>%
  filter(Parameter == "mean") %>%
  group_by(Variable, Gender, item) %>%
  summarize(MAP = estimate_mode(value),
            cred_upper = hdi_upper(value),
            cred_lower = hdi_lower(value)) %>%
  ungroup()

rs.habituals.bda.prior.summary.wide <- left_join(
  rs.habituals.bda.prior.summary %>% filter(Variable == "mix") %>%
    select(-Variable) %>%
    rename(mix_mean = MAP, mix_upper = cred_upper, mix_lower = cred_lower),
  rs.habituals.bda.prior.summary %>% filter(Variable == "stableFreq") %>%
    select(-Variable) %>%
    rename(sfreq_mean = MAP, sfreq_upper = cred_upper, sfreq_lower = cred_lower)
)

# for displaying in text
n.items.habituals.prior.modeling <- length(rs.habituals.bda.prior.summary.wide$item)

rs.habituals.bda.prior.summary.wide <- left_join(rs.habituals.bda.prior.summary.wide,
          d.hab.priors %>% select(item, category) %>% distinct())

figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.prior.summary.wide %>%
                                            mutate(Gender = factor(Gender, levels = c("male", "female"))),
       aes( x = mix_mean, xmin = mix_lower, xmax = mix_upper,
            y = sfreq_mean, ymin = sfreq_lower, ymax = sfreq_upper,
             fill = Gender, shape = Gender))+
  geom_errorbar(alpha = 0.5)+
  geom_errorbarh( alpha = 0.5)+
  scale_shape_manual(values=c(21,22))+
  #scale_color_solarized()+scale_fill_solarized()+
  scale_fill_brewer(palette='Set1')+
  #scale_color_brewer(palette='Set1')+
  geom_point(size=4, 
            #  inherit.aes = F, 
            #  aes(x = mix_mean,y = sfreq_mean,  fill = category,
            # shape = Gender),  
            alpha = 0.9)+

  xlab("% have DONE ACTION")+
  ylab("Frequency of DOING ACTION \n (log scale)")+
  #scale_
  coord_fixed(ratio = 1/8)+
  guides(fill = F,  shape = F)+
  theme(legend.title = element_blank(),#element_text(hjust=0),
        legend.position=c(0.82,0.14),
        legend.direction="vertical") +
        scale_y_continuous(limits = c(-1.5, 6.5), 
                     breaks = c(0, 2.5, 4, 5.9),
                     labels = c("annually", "monthly", "weekly", "daily"))+
  geom_text_repel(data = rs.habituals.bda.prior.summary.wide %>%
                    filter(item %in% example.habituals, Gender == "female"), 
                  inherit.aes =F,
                  aes(x = mix_mean,y = sfreq_mean, label = item), force = 5, size = 3)
```

```{r habituals-prior-model-forwardSample}
rs.habituals.bda.prior.spread <- rs.habituals.bda.prior %>% 
  mutate(param = paste(Variable, Parameter, sep = "_")) %>%
  select(-Variable, -Parameter, -Chain) %>%
  spread(param, value)

rs.habituals.bda.prior.samples <- data.frame()
for (i in 1:1){
  rs.habituals.bda.prior.samples <- bind_rows(
    rs.habituals.bda.prior.samples,
    rs.habituals.bda.prior.spread %>%
    rowwise() %>%
    mutate(
      a = mix_mean * mix_samplesize,
      b = (1 - mix_mean) * mix_samplesize,
      theta = rbeta(n = 1, shape1 = a, shape2 = b),
      stable = rbinom(n = 1, size = 1, prob = theta),
      logannualRate = ifelse(stable == 1, 
                             rnorm(n = 1, 
                                   mean = stableFreq_mean, 
                                   sd = stableFreq_sd), -5),
       annualRate =  exp(logannualRate)
    )
  )
}
```

```{r habituals-prior-marginals-fig, fig.width = 7, fig.cap="Reconstructed priors on frequency from the structured, prior elicitation task (Expt. 2a). Priors are reconstructed by bootstrapping and forward sampling using the structured model (data, blue) or using Bayesian data analysis on the structured model (model, red).", cache = F}

figure.habituals.priors.marginals <- bind_rows(
  d.hab.priors.samples %>% 
    mutate(src = 'data', 
           val = log(val)),
  rs.habituals.bda.prior.samples %>%
    rename(gender = Gender, val = logannualRate) %>%
    select(gender, item, val) %>%
    mutate(src = 'model')
  ) %>%
  filter(item %in% example.habituals,
         src == 'model') %>%
  mutate(item = factor(item, levels = example.habituals),
         gender = factor(gender, levels = c("male", "female"))) %>%
ggplot(. , aes( x = val, color = gender))+
  geom_density(size = 0.8, aes( y = ..scaled.. ))+
  facet_wrap(~item, nrow = 4)+
  scale_color_solarized()+
  xlab("Frequency")+
  ylab("Scaled probability density")+
  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
  theme(strip.text.y = element_text(angle = 0),
        legend.position = c(0.9, 0.11),
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 90))+
    scale_x_continuous(limits = c(-5, 8), 
                     breaks = c(-5, 0, 2.5, 4, 5.9),
                     labels = c("almost never", "annually", "monthly", "weekly", "daily"))

#figure.habituals.priors.marginals
```

```{r habituals-prior-figure, fig.width = 11, fig.height = 6, fig.cap="Prevalence priors for events (Expt. 2a). Left: Mean mixture parameter and mean stable frequency parameter for 31 events. Right: Inferred priors on frequencies from the structured, prior elicitation task. Priors are reconstructed by forward sampling using the inferred parameters in the prior mixture model.", cache = F}
grid.arrange(figure.habituals.priors.scatter, figure.habituals.priors.marginals, nrow = 1)
```

@@

```{r habituals-prior-mixture-summarize}
d.hab.priors.mixture.summary <- d.hab.priors.filtered %>%
  select(item, starts_with("mixture_")) %>%
  gather(key, value, -item) %>%
  group_by(item) %>%
  multi_boot_standard( col = 'value' )
```

@@

### Method
```{r habituals-endorsement}
d.hab.endorsement.catch <- read.csv(paste(project.path, "data/habituals/endorsement/", 
                    "habituals-endorsement-catch_trials.csv", sep = ""))

d.hab.endorsement <- read.csv(paste(project.path, "data/habituals/endorsement/", 
                    "habituals-endorsement.csv", sep = ""))

d.hab.endorsement <- left_join(
  left_join(d.hab.endorsement, 
           d.hab.endorsement.catch %>% 
             select(workerid, pass)
           ) %>%
  filter(pass == 1),
  d.hab.priors.mixture.summary %>% rename(habitual = item, mixture = mean, mix_low = ci_lower, mix_high = ci_upper)) %>%
  mutate(response = ifelse(as.character(response) == "agree-key", 1, 0)) %>%
  rowwise() %>%
  mutate(
    annualRate = annualRates[[as.character(time_period)]]*n_instances,
    logAnnualRate = log(annualRate)
  )

d.hab.endorsement.bayes <- d.hab.endorsement %>% 
  group_by(habitual, logAnnualRate, time_period) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

example.habituals <- c("climbs mountains_year", "hikes_year", "runs_year",
                       "goes to the movies_month", "smokes cigarettes_month")
fig.habituals.endorsement.vs.freq <- 
  ggplot(d.hab.endorsement.bayes, aes( x = logAnnualRate, y = MAP_h, ymin = low, ymax = high, fill = logAnnualRate))+
  geom_jitter(width = 0.1, shape = 21, size = 5)+
  ylab("Human endorsement probability")+
  xlab("Frequency of target")+
  geom_label_repel(data = d.hab.endorsement.bayes %>% 
                    mutate(sentence = paste(habitual, time_period, sep = "_")) %>%
                    filter(sentence %in% example.habituals), aes( label = habitual ),
                       color = 'black', fill = 'white',
    box.padding = unit(0.35, "lines"),
    point.padding = unit(1e-06, "lines"),
    segment.color = 'grey37', segment.size=0.7, nudge_x= 1.1, nudge_y = -0.1)+
  scale_x_continuous(limits = c(-1,6), 
                     breaks = c(-1, 0, 0.7, 2.5, 4, 5.9),
                     labels = c("three years", "annually", "bi-annually", "monthly", "weekly", "daily"))+
  scale_y_continuous(limits = c(-0.01, 1.01), 
                     breaks = c(0, 0.5, 1))+
  scale_fill_continuous(breaks = c(0, 5))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        legend.position = "bottom")+
  coord_fixed(ratio = 7)+
  guides(fill = guide_colorbar(title = 'log annual rate',
                               ticks = F))
```

Each event from Expt. 2a was then paired with between 2 - 4 frequencies, for which the habitual statement would be evaluated. 
Frequencies were always "3 times every \textsc{time period}" so that the referent character had always completed the event multiple times.
\textsc{time period}s were chosen specific to each event by simulating predictions of the endorsement model (Eq. \ref{eq:S1}) with the goal of maximizing the variability in endorsements across items.
For example, relatively high frequencies were chosen (e.g., three times every week vs. 2 months) for an item that was expected to occur rather often (e.g., "runs") because the model predicted that much of the variability in endorsement would occur in this range; for an item was expected to occur infrequently (e.g., "climbs mountains"), lower frequencies were chosen (e.g., three times every 5 years vs. 2 years).
In total, `r nrow(d.hab.endorsement %>% select(habitual, time_period) %>% distinct())` unique items were created by pairing frequencies with events.

```{r habituals-items-table, eval = F}
d.hab.endorsement.items <- select(d.hab.endorsement, habitual, time_period) %>% distinct()

d.hab.endorsement.items[with(d.hab.endorsement.items, order(habitual)), ] %>% 
  kable(., 
        format = "latex", longtable = T, booktabs = T,
        caption = "Demo table") %>% 
  kable_styling(latex_options = c("repeat_header"),
                font_size = 7)#%>%#, "hold_position")) %>%
  #column_spec(3, width = "10cm")%>%
  #collapse_rows(columns = 1:2)
```

```{r habituals-endorsement-gender-exploration-scatter, fig.cap='Exploratory analysis of endorsements of habitual statements by gender of target character (e.g., "Mary drinks beer" vs. "John...") for six events that displayed appreciable differences in the prior elicitation. Labeled points all correspond to the time period of 3 times / month.'}
gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                    "wears a bra", "wears a watch", "wears a suit")

d.hab.bayes.gendered <- d.hab.endorsement %>%
  #filter(habitual %in% gendered.items) %>%
  group_by(habitual, characterGender, time_period) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

d.hab.bayes.gendered.wide <- left_join(
    d.hab.bayes.gendered %>%
    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
    filter(characterGender == "female") %>%
    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
    select(-characterGender),
  d.hab.bayes.gendered %>%
    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
    filter(characterGender == "male") %>%
    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
    select(-characterGender)
)

@@

d.hab.bayes.gendered.subset <- d.hab.endorsement %>%
  filter(habitual %in% gendered.items) %>%
  group_by(habitual, characterGender, time_period) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

d.hab.bayes.gendered.subset.wide <- left_join(
    d.hab.bayes.gendered.subset %>%
    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
    filter(characterGender == "female") %>%
    rename(map_female = MAP_h, low_female = low, high_female = high) %>%
    select(-characterGender),
  d.hab.bayes.gendered.subset %>%
    select(habitual, characterGender, time_period, MAP_h, low, high) %>%
    filter(characterGender == "male") %>%
    rename(map_male = MAP_h, low_male = low, high_male = high) %>%
    select(-characterGender)
)

n.habituals.gendered.subset.analysis <- length(d.hab.bayes.gendered.subset.wide$habitual)
r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, cor(map_female, map_male)), 3)

# ggplot(d.hab.bayes.gendered.wide, aes( x = map_female, y = map_male,
#                  xmin = low_female, ymin = low_male,
#                  xmax = high_female, ymax = high_male, fill = habitual))+
#   geom_text_repel(data = d.hab.bayes.gendered.wide %>%
#                     filter(time_period== "month"), aes(label = habitual,
#                                                        color = habitual),
#                   force = 3, nudge_x = -1, segment.size = 0.3)+
#   guides(fill = F, color = F)+
#   geom_abline(intercept = 0, slope = 1, lty = 3)+
#   geom_point(shape = 21)+
#   geom_errorbar(alpha = 0.3) + geom_errorbarh(alpha = 0.3)+
#   scale_x_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
#   scale_y_continuous(limits = c(0,1), breaks = c(0,0.5,1))+
#   coord_fixed()+
#   xlab("Habitual endorsement (female character)")+
#   ylab("Habitual endorsement (male character)")+
#   scale_fill_solarized()+
#   scale_color_solarized()
# r2.habituals.gendered
#n.habituals.gendered.subset.analysis
#r.habituals.gendered.subset.analysis
```

```{r habituals-endorsement-gender-exploration, results="asis", eval = F}
gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                    "wears a bra", "wears a watch", "wears a suit")

d.hab.bayes.gendered <- d.hab.endorsement %>%
  filter(habitual %in% gendered.items) %>%
  group_by(habitual, characterGender) %>%
  summarize(k = sum(response), n = n()) %>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         low  = qbeta(.025, a, b),
         high = qbeta(.975, a, b),
         MAP_h = (a-1)/(a+b-2),
         mean = a / (a + b))

left_join(
    d.hab.bayes.gendered %>%
    select(habitual, characterGender, MAP_h, low, high) %>%
    filter(characterGender == "female") %>%
    mutate(female = paste(as.character(round(MAP_h, 2)), " [",
                        as.character(round(low, 2)), ", ",
                        as.character(round(high, 2)), "]", sep = "")) %>%
    select(-MAP_h, -low, -high,  -characterGender),
  d.hab.bayes.gendered %>%
    select(habitual, characterGender, MAP_h, low, high) %>%
    filter(characterGender == "male") %>%
    #rename(male_MAP, male_low = low, male_high = high) %>%
    mutate(male = paste(as.character(round(MAP_h, 2)), " [",
                        as.character(round(low, 2)), ", ",
                        as.character(round(high, 2)), "]", sep = "")) %>%
    select(-MAP_h, -low, -high, -characterGender)
    #rename(female_MAP, female_low = low, female_high = high)
) %>% xtable(.,
         caption = c("Exploratory analysis of endorsements of habitual statements by gender for six properties of interest, collapsed across frequencies."),
        label = c("tab:habituals-endorsement-gender")) %>%
print(., type = "latex", 
      tabular.environment = "tabularx", width = "\\textwidth",
      scalebox='0.75',
      include.rownames = FALSE, comment = F)
```

```{r habituals-regression-models}

glm.hab.endorse.freq <- glm(response ~ logAnnualRate, 
              data = d.hab.endorsement, family = 'binomial')

glm.hab.endorse.freq.distinct <- glm(response ~ logAnnualRate + mixture, 
              data = d.hab.endorsement, family = 'binomial')

d.hab.endorse.freq.mix.uniq <- unique(select(
    d.hab.endorsement, habitual, logAnnualRate, time_period, 
    mixture, mix_low, mix_high
  ))

d.hab.endorse.freq.mix.uniq.lower <- d.hab.endorse.freq.mix.uniq %>% 
  select(-mixture) %>% 
  rename(mixture = mix_low)

d.hab.endorse.freq.mix.uniq.upper <- d.hab.endorse.freq.mix.uniq %>% 
  select(-mixture) %>% 
  rename(mixture = mix_high)

d.hab.endorse.regression.freq <- left_join(
  d.hab.endorsement.bayes,
  d.hab.endorse.freq.mix.uniq %>%
    mutate(
      prediction = predict(glm.hab.endorse.freq, ., type = "response"), 
      prediction_lower = prediction,
      prediction_upper = prediction,
      src = "regression_freq"
      )
)

@@

# n.b.: Since distinctiveness is being captured by "mix", the lower the "mix", the higher the endorsement. Thus, lower bound of errorbars are computed with upper estimate of "mix"
d.hab.endorse.regression.freq.mix <- left_join(
  d.hab.endorsement.bayes,
  d.hab.endorse.freq.mix.uniq %>%
    mutate(
      prediction = predict(glm.hab.endorse.freq.distinct, ., type = "response"),
      prediction_lower =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.upper, type = "response"),
      prediction_upper =  predict(glm.hab.endorse.freq.distinct, d.hab.endorse.freq.mix.uniq.lower, type = "response"),
      src = "regression_freq_distinct"
      )
)

@@

d.hab.endorse.regression <- bind_rows(d.hab.endorse.regression.freq, d.hab.endorse.regression.freq.mix) %>%
  mutate(sqErr = (MAP_h-prediction)^2)

# ggplot(d.hab.endorse.regression,
#        aes (x = prediction, y = MAP_h, ymin = low, ymax = high, color = mixture))+
#   geom_errorbar(alpha = 0.1)+
#   geom_abline(intercept = 0, slope = 1, lty = 3)+
#   # geom_text_repel(data = d.hab.endorse.regression.freq.distinct %>%
#   #                   filter(sqErr > 0.1),
#   #                 aes(label = paste(habitual, time_period)), force = 5, size = 3)+
#   geom_point()+
#   xlim(0,1)+
#   ylim(0,1)+
#   coord_fixed()+
#   xlab("Logistic model prediction")+
#   ylab("Human habitual endorsement")+
#   facet_wrap(~src)

# with(d.hab.endorse.regression %>%
#        filter(src == "regression_freq"), 
#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
# 
# with(d.hab.endorse.regression %>%
#        filter(src == "regression_freq_distinct"), 
#      cor(prediction, MAP_h, use = "pairwise.complete.obs"))^2
```

```{r habituals-fullmodel, fig.width = 8}
n_chains <- 3
n_samples <- 100000
burn <- n_samples / 2
lg <- 20
model_prefix <- "results-habituals-jointModel-S1-"

# m.hab.samp <- data.frame()
#  m.hab.fixed.samp <- data.frame()

#for (i in seq(1, n_chains)){
  # mi <- fread(paste(project.path,  "models/habituals/results/",
  #                   model_prefix, "smtncs_habitual-",
  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
  # m.hab.samp <- bind_rows(m.hab.samp, mi %>% mutate(chain = i))

  # mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
  #                   model_prefix, "smtncs_some-",
  #                   n_samples, "_burn", burn, "_lag", lg, "_chain", i, ".csv", sep = ""))
#   mi.fixed <- fread(paste(project.path,  "models/habituals/results/",
#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain", i, ".csv", sep = ""))
#   #
#   m.hab.fixed.samp <- bind_rows(m.hab.fixed.samp, mi.fixed %>% mutate(chain = i))
# }

# save(m.hab.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
# 
# save(m.hab.fixed.samp,
#      file = paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# save(m.hab.fixed.samp,
#      file = paste(project.path,  "models/habituals/results/results-habituals-jointModel-inferFixedThreshold-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

load(paste(project.path,  "models/habituals/results/", model_prefix, "habitual-",
                    n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))

# load(paste(project.path,  "models/habituals/results/", model_prefix, "some-",
#                     n_samples, "_burn", burn, "_lag", lg, "_",n_chains , "chains.RData", sep = ""))
load(paste(project.path,
           "models/habituals/results/results-habituals-jointModel-inferFixedThreshold-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))
# load(paste(project.path,  "results-habituals-jointModel-inferFixedThresholdCts-noise-S1-smtncs_some-100000_burn50000_lag20_2chains.RData", sep = ""))

# m.hab.fixed.samp <- fread(paste(project.path,  "models/habituals/results/",
#                           "results-habituals-jointModel-inferFixedThreshold-S1-smtncs_some-100000_burn50000_lag20_chain1.csv", sep = ""))

fixed.hab.params.posterior <-  m.hab.fixed.samp %>% 
  filter(type == "param") %>%
  #filter(B %in% c("noise", "fixedThreshold")) %>%
  group_by(B) %>% 
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

hab.uncertain.threshold.s1opt <- m.hab.samp %>% 
  filter(type == "param") %>%
  group_by(B) %>%
  summarize(MAP = estimate_mode(val),
            cred_upper = hdi_upper(val),
            cred_lower = hdi_lower(val))

>>>>

```{r habituals-priors-subfigs, fig.width = 8}
example.habituals <- c("smokes marijuana", "smokes cigarettes","drinks coffee",
                       "climbs mountains", "hikes", "runs", 
                       "wears a suit", "wears a watch", "wears socks", 
                       "writes poems", "goes to the movies", "plays the banjo"
                       )
annualRates = list("5 years" = 1/5, "2 years" = 1/2,
                   "year" = 1, "6 months" = 2, "2 months" = 6,
                   "month" = 12, "2 weeks" = 26 ,"week" = 52)

load("cached_results/case2_priors_parametersPredictives.RData") #habituals.priors.marginals, rs.habituals.bda.posterior.predictive.measurementSpace, rs.habituals.bda.prior.summary.wide

n.items.habituals.prior.modeling <- length(rs.habituals.bda.prior.summary.wide$item)

figure.habituals.priors.scatter <- ggplot(rs.habituals.bda.posterior.predictive.measurementSpace,
       aes(x = MAP, xmin = cred_lower, xmax = cred_upper,
           y = empirical_mean, ymin = ci_lower, ymax = ci_upper, color = gender))+
  facet_wrap(~measurement, scales = 'free', nrow = 2)+
  scale_color_solarized()+
  geom_errorbar(alpha = 0.3)+geom_errorbarh(alpha = 0.3)+
    geom_label_repel(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
                    filter(item %in% example.habituals, gender == "female"), 
                  inherit.aes =F,
                  aes(x = MAP,y = empirical_mean, label = item), force = 15, size = 3)+
  geom_point()+
  coord_fixed()+
  xlab("Model posterior predictive")+
  ylab("Empirical means")+
  theme(legend.position = c(0.86, 0.09))

figure.habituals.priors.marginals <- ggplot(habituals.priors.marginals %>%
  filter(val > -4.9) %>%
  mutate(gender = factor(gender, levels = c("female", "male"))), 
  aes( x = val, color = gender, lty = src))+
  geom_density(size = 0.4, aes( y = ..scaled.. ))+
  facet_wrap(~item, nrow = 4)+
  geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
               filter(gender == 'male', measurement == "% people who have done action before"), 
            aes(xmin = -5, xmax = -4.5, ymin = 0, ymax = MAP),
              fill = "#268bd2", 
            color = 'black',
             inherit.aes = F)+
  geom_rect(data = rs.habituals.bda.posterior.predictive.measurementSpace %>%
               filter(gender == 'female', measurement == "% people who have done action before"), 
            aes(xmin = -4.25, xmax = -3.75,
                                            ymin = 0, ymax = MAP),
            fill = "#cb4b16",
            color = 'black',
             inherit.aes = F)+
  scale_color_solarized()+
  xlab("Frequency")+
  ylab("Scaled probability density")+
  scale_y_continuous(limits = c(0,1), breaks = c(0, 1)) +
  theme(legend.position = c(0.93, -0.1),
        legend.title = element_blank(),
        legend.box = 'vertical',
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1),
        legend.margin=margin(t=0, r=0, b=-0.25, l=0, unit="cm"),
    strip.text = element_text(size = 7))+
  scale_x_continuous(
      limits = c(-5, 8),
      breaks = c(-5, 0, 2.5, 4, 5.9),
      labels = c("almost never", "annually", "monthly", "weekly", "daily")
      )+
  guides(color = F)
```

```{r habituals-prior-figure, fig.width = 15,fig.asp = 0.37, fig.cap="Prevalence priors for events (Expt. 2a). A: Mixture-model posterior predictions in comparison to the empirical mean responses for the two prior elicitation questions. Items cover the full spectrum of possible parameter values. B: Reconstructed prevalence priors. In order to show frequencies for events that are very rare across people (e.g., \"writes novels\"), extremely low frequencies (\\emph{almost never}) are omitted. Instead, height of the bars on left denote the Maximum A-Posteriori values of the mixture component (same as the \\emph{proportion of people who have done action before} scatter-plot), reflecting the (inverse) rarity of the event across people.", cache = F}
cowplot::plot_grid(
  figure.habituals.priors.scatter + theme(plot.margin = unit(c(6,6,6,0), "pt")), 
  figure.habituals.priors.marginals + theme(plot.margin = unit(c(6,0,6,6), "pt")),
  labels = c("A", "B"), #nrow = 1,
  align = 'h',
  rel_widths = c(1, 3)
  )
```

@@

@@

```{r habituals-endorsement-gender-exploration}
load("cached_results/case2_endorsement_genderItemAnalysis.RData") #d.hab.bayes.gendered.wide, d.hab.bayes.gendered.subset.wide
gendered.items <- c("does cocaine", "drinks beer", "drinks coffee",
                    "wears a bra", "wears a watch", "wears a suit")

@@

n.habituals.gendered.subset.analysis <- length(d.hab.bayes.gendered.subset.wide$habitual)
r.habituals.gendered.subset.analysis <- round(with(d.hab.bayes.gendered.subset.wide, 
                                                   cor(map_female, map_male)), 3)
```

```{r habituals-regression-models}
load("cached_results/case2_endorsement_regressionResults.RData") #d.hab.endorse.regression.freq.mix, d.hab.endorse.regression.freq, d.hab.endorse.regression

@@

@@

```{r habituals-rsamodels}
load("cached_results/case2_endorsement_rsaModelResults.RData") #m.hab.endorse.rsa, hab.uncertain.threshold.s1opt, fixed.hab.params.posterior, md.hab.long, hab.listener.predictions

## model parameters
fixed.threshold.hab.posterior <- filter(fixed.hab.params.posterior, B == "fixedThreshold")
fixed.noise.hab.posterior <- filter(fixed.hab.params.posterior, B == "noise")
hab.fixed.threshold.s1opt <- filter(fixed.hab.params.posterior, B == "speakerOptimality")
